Summary Tables

### 2020-11-18 summary_tables.Rmd
Add baseline duration

@@

@@

>>>>

trip_dur <- list()

l <- list()

@@

  l[[city]] <- td

  if (length(trip_dur) == 0){
    trip_dur <- td1 %>% dplyr::select(stage_mode)
  }

  trip_dur <- inner_join(trip_dur, td1, by = 'stage_mode')

@@

### Baseline average duration (mins) per day for all case studies
```{r}

trip_dur <- trip_dur %>% janitor::adorn_totals('row')

kable(trip_dur, caption = "Avg. duration per person (mins) per day across all case studies")
